### 2014-01-30 docs/paper/paper.tex
future work, partial

\begin{itemize}
\item board-to-board communication for larger networks
\item increase design size by using off-chip memory (DDR3)
\item better network stack to allow control and I/O over common protocols e.g. UDP
\end{itemize}

>>>>

\begin{itemize}
\item board-to-board communication for larger networks

The flexibility of input and output channels lends to their use in connecting multiple devices together for use as part of a larger simulation engine.
This would allow networks to be simulated that consume more resources than are available on a single device, which may in turn allow
for ``grids'' of inexpensive hardware devices to be used to simulate a very large model.
\item increase design size by using off-chip memory (DDR3)
\item better network stack to allow control and I/O over common protocols e.g. UDP

The current control and I/O interface communicates over Ethernet, but since bare frames are being used with no higher-level protocols on top of them,
it is somewhat cumbersome to set up a computer or other device to send and receive data to the hardware.
This approach is suitable for testing and prototyping, but it makes certain assumptions about the setup of the network and the host computer that
may not be reasonable for general use, such as requiring raw socket privileges on the host operating system (which typically require administrator access).
A more user-friendly approach would be to implement an Ethernet stack that supports a protocol such as UDP, which can be readily used by many different
kinds of host software in order to interact with a simulation.
\end{itemize}
